A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-14 paper/ms.tex
update ms
Co-authored-by: gummiks <gstefansson@astro.princeton.edu>

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.3\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler satellite because it is nearby
  ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Here we show that
  Kepler\,1627 is a member of the \clusterage\ old $\delta$~Lyr
  cluster, based on Gaia kinematics, TESS stellar rotation
  periods, and spectroscopic lithium abundances.  To
  our knowledge, Kepler\,1627Ab is the youngest planet with a precise
  age yet found by the main Kepler mission.  From unresolved
  starspot-crossing events in the Kepler photometry and
  a Keck/HIRES transit we find that the planet is likely on an
  orbit aligned with the stellar spin axis.  We also briefly explore the flare
  arrival time distribution in the short cadence Kepler
  photometry.
  The $\delta$~Lyr cluster is one of many stellar groups whose
  properties have been clarified using Gaia; many other new
  clusters also overlap with confirmed and candidate exoplanets.
  Verifying the results of Gaia clustering analyses using TESS rotation
  periods seems to be a promising path toward expanding the census of
  age-dated planets, and our corresponding understanding of planetary evolution.
\end{abstract}

@@

%TODO: might want to revise this text to better frame the boil-off phase...
%TODO: better citations on radius evolution?
For instance, the ``mini-Neptunes'', thought to be made of molten
rocky cores \citep{kite_atmosphere_2020} and extended atmospheric
envelopes of hydrogen and helium, are expected to shrink in size by
factors of several over their first $10^8$ years
\citep{owen_atmospheres_2016,owen_constraining_2020}.  Specifically,
they start with sizes of 4--12\,$R_\oplus$ shortly after the time of disk
dispersal ($\lesssim$$10^7$\,years), and shrink to sizes of
2--4\,$R_\oplus$ by 10$^8$ years.  While the majority of this change
is expected to occur within the first few million years of disk
dispersal \citep{owen_atmospheres_2016}, the combination of stellar
irradiation and internal heat may also power a more
gradual outflow which can eventually deplete or entirely strip the
envelope from the rocky core
\citep{Owen_Wu_2013,ginzburg_corepowered_2018}.  Discovering young
planets, measuring their masses, and detecting their atmospheric
outflows are key steps toward testing this paradigm, which is often
invoked to explain the observed radius distribution of mature
exoplanets \citep{Fulton_et_al_2017}.

@@

A previous clustering analysis of the Gaia data reported that
Kepler\,1627 (KIC 6184894; KOI 5245; TIC 120105470) is a member of the
\cn\ \citep{kounkel_untangling_2019}.  Given the previous statistical
validation the close-in mini-Neptune Kepler 1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we examined the age of the star and its putative host cluster more
closely (Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr
cluster is \clusterage\ old, and that \sn\ is indeed a member of the
cluster.  Focusing on the planet itself, we confirm that despite the
presence of a previously unreported binary companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary on an orbit that
is likely aligned with the stellar rotation axis
(Section~\ref{sec:planet}).  We conclude by highlighting broader
implications for our ability to age-date a statistical sample of
planets (Section~\ref{sec:conc}).

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler and TESS views of the $\delta$\,Lyr cluster.} Colored
    points are kinematically selected members of the $\delta$\,Lyr
    cluster.  Both Kepler (gray squares) and TESS observed portions of
    the cluster.  Naked-eye stars ($m_{\rm V}<6.5$) are shown in gray;
    four of them (orange circles) are annotated.
    Kepler\,1627 (green star) was observed during the entirety of the
    Kepler mission, and has been observed by TESS for two lunar months
    to date.  The colors of the other cluster members indicate the
    number of TESS sectors during which they have been observed.
    \label{fig:skychart}
	}
\end{figure}

@@

We fitted the RVs using the \citet{hirano_analytic_2010,hirano_2011}
models for the Rossiter-McLaughlin (RM) effect, and allowed the
sky-projected obliquity, the stellar equatorial velocity, and the
Gaussian dispersion of the spectral lines to vary.  We also allowed
for an optional linear and quadratic trend, and a white-noise jitter
term.  The quadratic model with the RM effect is shown in
Figure~\ref{fig:obliquity}; the prior on $v\sin i$ has been assumed
from Table~\ref{tab:starparams}, and the jitter term has been
incorporated.
We found $\chi^2_{\rm red} =
5.4$ for the best-fitting linear case, and $\chi^2_{\rm red} = 4.4$
for the best-fitting quadratic, with a $\Delta {\rm BIC} = {\rm
BIC}_{\rm line} - {\rm BIC}_{\rm quad} = 19.6$ and $\Delta {\rm AIC} =
{\rm AIC}_{\rm line} - {\rm AIC}_{\rm quad} = 20.6$.  While this
provides strong statistical evidence to prefer the quadratic model
over the linear one, the $\chi^2_{\rm red}$ indicate that neither fit
is very good.  Considering a quadratic trend without any RM
effect yields $\chi^2_{\rm red} = 4.3$, and $\Delta {\rm BIC} = {\rm
BIC}_{\rm trend} - {\rm BIC}_{\rm quad} = 1.9$ ($\Delta {\rm
AIC}=5.2$).  From a model-comparison standpoint, there is therefore
only marginal statistical evidence to prefer the best-fitting ``RM and
quadratic trend'' model over the best-fitting ``quadratic trend only''
model.  Given the expected semi-amplitude of the velocity anomaly
($\Delta v_{\rm RM}\approx 20\,{\rm m\,s}^{-1}$) and the achieved precision,
we cannot claim a detection of the Doppler transit.
From the MuSCAT3 data however, we do know that the transit
was observed, and the increase in radial velocity seen shortly after
ingress is more consistent with a prograde or polar orbit than a
retrograde orbit.  Fixing the orbit to be either exactly prograde or
exactly retrograde, we find $\Delta {\rm BIC} = {\rm BIC}_{\rm
retrograde} - {\rm BIC}_{\rm trend} = 18.0$; the retrograde case is
ruled out on this basis.
% More data will be needed however to
% make a more precise measurement of the stellar obliquity.

@@

\software{
  %\texttt{arviz} \citep{arviz_2019},
  \texttt{altaipony} \citep{ilin_flares_2021},
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  %\texttt{astroplan} \citep{astroplan2018},
	%\texttt{AstroImageJ} \citep{collins_astroimagej_2017},
  \texttt{astropy} \citep{astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
  %\texttt{ceres} \citep{brahm_2017_ceres},
  %\texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019},
  \texttt{corner} \citep{corner_2016},
  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
  dependencies \citep{exoplanet:agol20, exoplanet:kipping13, exoplanet:luger18,
   	exoplanet:theano},
	%\texttt{gala} \citep{gala,PriceWhelan_2017_gala_zenodo},
	%\texttt{IDL Astronomy User's Library} \citep{landsman_1995},
  \texttt{IPython} \citep{perez_2007},
	%\texttt{isochrones} \citep{morton_2015_isochrones},
	%\texttt{lightkurve} \citep{lightkurve_2018},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  %\texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  %\texttt{pyGAM} \citep{serven_pygam_2018_1476122},
  \texttt{PyMC3} \citep{salvatier_2016_PyMC3},
  %\texttt{radvel} \citep{fulton_radvel_2018},
  %\texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001},
  \texttt{TESS-point}  \citep{burke_2020},
  %\texttt{tesscut} \citep{brasseur_astrocut_2019},
	%\texttt{VESPA} \citep{morton_efficient_2012,vespa_2015},
  %\texttt{webplotdigitzer} \citep{rohatgi_2019},
  \texttt{wotan} \citep{hippke_wotan_2019}.
}
\

@@

The \texttt{v0.6} CDIPS target catalog (Table~\ref{tab:v06}) includes
stars that are young, age-dated, and age-dateable.  By ``age-dateable'',
we mean that the age should be measurable at greater
precision than a typical FGK field star.
As in
\citet{bouma_cdipsI_2019}, we collected stars that met these criteria
from across the literature.  Table~\ref{tab:metadata} gives a list of
the studies included, and brief summary statistics.
The age measurement methodologies adopted by each study differ: in many,
spatial and kinematic clustering has been performed on the Gaia data,
and ensemble isochrone fitting of the resulting clusters has been performed
(typically focusing on the turn-off).
In other studies however, the claim of youth is based on the location of a
single star in the color-absolute magnitude diagram, or on spectroscopic
information.

@@

Figure~\ref{fig:XYZvtang} shows stars reported by
\citet{kounkel_untangling_2019} to be in the group ``Theia 73'', which
was cross-matched by Kounkel \& Covey as being ``Stephenson 1''.
\citet{kounkel_untangling_2019} reported \noriginal\ stars to be
present in this cluster.  For our Figure, galactic positions were
calculated and plotted only for stars with parallax signal-to-noise
exceeding 20.  The location of the Sun is shown on the plots.  The
smattering of reported cluster members (gray and black points) has a
significantly different structure that the cluster initially
identified by \citet{stephenson_possible_1959} and corroborated by
\citet{eggen_photometric_1968}.  While the non-uniform ``clumps''
might be part of a real structure, they could also be an artifact of
the data processing steps performed by
\citet{kounkel_untangling_2019}.  We therefore opted to only consider
stars in the immediate kinematic and spatial vicinity of \sn.  The
tangential velocities relative to \sn\ are shown in the bottom right
panel.  These are computed by assuming that every star has the same
three-dimensional spatial velocity as \sn, where we assume a systemic
radial velocity of $-16.7 \pm 0.2$\,\kms\ based on the HIRES
spectra.  The
relevant projection effects are then taken into account, as discussed
by {\it e.g.}, \citet{Meingast2021} and \citet{bouma_2021_ngc2516}.
We performed the actual selection by then manually drawing lassos with
the interactive \texttt{glue} visualization tool
\citep{beaumont_2014_13866} in the four projections shown in
Figure~\ref{fig:XYZvtang}.  While cluster members likely exist
outside of our selection region (and our selection also includes some
field star interlopers), our aim is to verify the existence of the
cluster in the vicinity of Kepler\,1627, and to measure its age.  The
procedure we have adopted enables both tasks.

@@

		\vspace{-0.1cm}
		\subfloat{
			\includegraphics[width=0.55\textwidth]{f6.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler 1627 is a binary.} {\it Top:} High-resolution imaging
    from Gemini-North/`Alopeke ({\it left}) and Keck/NIRC2 ({\it
    right}) shows an $\approx$M2V companion at $\rho \approx
    0\farcs16$, which corresponds to a projected separation of
    $53\pm4$\,au.  {\it Bottom:} Gaia EDR3 renormalized unit weight
    error (RUWE) point estimates for Kepler\,1627A and other members
    of the $\delta$\,Lyr cluster reported by \citet{KounkelCovey2019}.
    Since other members of the cluster with similar colors have
    comparable degrees of photometric variability, the high RUWE
    suggests that Kepler\,1627 is an astrometric binary. 
    \label{fig:kep1627binary}
	}
\end{figure*}

@@

Figure~\ref{fig:flarestats} shows the results.  The vertical lines in
the figure show the planetary orbital period, the synodic period
$P_{\rm syn} = (P_{\rm rot}^{-1} - P_{\rm orb}^{-1})^{-1}$, and linear
combinations thereof.  Note that the tidal period (half the synodic
period) is not shown.  The bins are logarithmically spaced to give 100
bins between the minimum and maximum ordinate values.  The gray bands
express the range of values observed from the Poissonian draws.  While
it does seem like an odd coincidence for peaks in the observed
flare arrival time distribution to coincide with the locations of
these ``special intervals'', the statistical evidence for a
non-Poissonian process driving the flares does not seem especially
overwhelming.  More quantitatively, the peaks observed at the orbital and
synodic periods are within the $\pm 2$-$\sigma$ range of a Poissonian
process, and those at $P_{\rm orb}+P_{\rm syn}$ and $P_{\rm
orb}+2P_{\rm syn}$ are only slightly above this range.  With that
said, future analyses of these data by investigators with more
knowledge of this topic could very well yield more quantitative
insights.

>>>>

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.3\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler satellite because it is nearby
  ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Here we show that
  Kepler\,1627 is a member of the \clusterage\ old $\delta$~Lyr
  cluster, based on Gaia kinematics, TESS stellar rotation periods,
  and spectroscopic lithium abundances.  To our knowledge,
  Kepler\,1627Ab is the youngest planet with a precise age yet found
  by the main Kepler mission.  From unresolved starspot-crossing
  events in the Kepler photometry and a Keck/HIRES transit we find
  that the planet is likely on an orbit aligned with the stellar spin
  axis.  We also briefly explore the flare arrival time distribution
  in the short cadence Kepler photometry.  The $\delta$~Lyr cluster is
  one of many stellar groups whose properties have been clarified
  using Gaia; many other new clusters also overlap with confirmed and
  candidate exoplanets.  Verifying the results of Gaia clustering
  analyses using TESS rotation periods offers a promising path toward
  expanding the census of age-dated planets, and our corresponding
  understanding of planetary evolution.
\end{abstract}

@@

%TODO: might want to revise this text to better frame the boil-off phase...
%TODO: better citations on radius evolution?
For instance, the ``mini-Neptunes'', thought to be made of molten
rocky cores \citep{kite_atmosphere_2020} and extended atmospheric
envelopes of hydrogen and helium, are expected to shrink in size by
factors of several over their first $10^8$ years.  Specifically, in
the models of \citet{owen_atmospheres_2016} and
\citet{owen_constraining_2020}, the $\approx5\,M_\oplus$ planets start
with sizes of 4--12\,$R_\oplus$ shortly after the time of disk
dispersal ($\lesssim$$10^7$\,years), and shrink to sizes of
2--4\,$R_\oplus$ by 10$^8$ years.  While the majority of this change
is expected to occur within the first few million years of disk
dispersal \citep{owen_atmospheres_2016}, the combination of stellar
irradiation and internal heat may also power a more gradual outflow
which can eventually deplete or entirely strip the envelope from the
rocky core \citep{Owen_Wu_2013,ginzburg_corepowered_2018}.
Discovering young planets, measuring their masses, and detecting their
atmospheric outflows are key steps toward testing this paradigm, which
is often invoked to explain the observed radius distribution of mature
exoplanets \citep{Fulton_et_al_2017}.

@@

A previous clustering analysis of the Gaia data reported that
Kepler\,1627 (KIC 6184894; KOI 5245; TIC 120105470) is a member of the
\cn\ \citep{kounkel_untangling_2019}.  Given the previous statistical
validation of the close-in mini-Neptune Kepler 1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we examined the age of the star and its putative host cluster more
closely (Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr
cluster is \clusterage\ old, and that \sn\ is indeed a member of the
cluster.  Focusing on the planet itself, we confirm that despite the
presence of a previously unreported binary companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary on an orbit that
is likely aligned with the stellar rotation axis
(Section~\ref{sec:planet}).  We conclude by highlighting broader
implications for our ability to age-date a statistical sample of
planets (Section~\ref{sec:conc}).

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler and TESS views of the $\delta$\,Lyr cluster.} Colored
    points are kinematically selected candidate $\delta$\,Lyr
    cluster members.  Both Kepler (gray panels) and TESS observed portions of
    the cluster.  Naked-eye stars ($m_{\rm V}<6.5$) are shown in gray or orange.
    Kepler\,1627 (green star) was observed during the entirety of the
    Kepler mission.  Colors of candidate cluster members indicate the
    duration of TESS observations to date.  So far, Kepler\,1627 has been
    observed by TESS for two lunar months.
    \label{fig:skychart}
	}
\end{figure}

@@

We fitted the RVs using the \citet{hirano_analytic_2010,hirano_2011}
models for the Rossiter-McLaughlin (RM) effect, 
following the methodology developed by \citet{stefansson_2020}.
We allowed the sky-projected obliquity, the projected stellar equatorial
velocity, and the Gaussian dispersion of the spectral lines to vary, and fixed the limb-darkening
using the $V$-band tabulation from \citet{claret_gravity_2011}.  We also
allowed
for an optional linear and quadratic trend, and a white-noise jitter
term.  The quadratic model with the RM effect is shown in
Figure~\ref{fig:obliquity}; the prior on $v\sin i$ has been assumed
from Table~\ref{tab:starparams}, and the jitter term has been
incorporated.
We found $\chi^2_{\rm red} =
5.4$ for the best-fitting linear case, and $\chi^2_{\rm red} = 4.4$
for the best-fitting quadratic, with a $\Delta {\rm BIC} = {\rm
BIC}_{\rm line} - {\rm BIC}_{\rm quad} = 19.6$ and $\Delta {\rm AIC} =
{\rm AIC}_{\rm line} - {\rm AIC}_{\rm quad} = 20.6$.  While this
provides strong statistical evidence to prefer the quadratic model
over the linear one, the $\chi^2_{\rm red}$ indicate that neither fit
is very good.  Considering a quadratic trend without any RM
effect yields $\chi^2_{\rm red} = 4.3$, and $\Delta {\rm BIC} = {\rm
BIC}_{\rm trend} - {\rm BIC}_{\rm quad} = 1.9$ ($\Delta {\rm
AIC}=5.2$).  From a model-comparison standpoint, there is therefore
only marginal statistical evidence to prefer the best-fitting ``RM and
quadratic trend'' model over the best-fitting ``quadratic trend only''
model.  Comparing the expected semi-amplitude of the velocity anomaly
for a well-aligned orbit ($\Delta v_{\rm RM}\approx 20\,{\rm m\,s}^{-1}$) with the achieved precision,
we cannot claim a detection of the Doppler transit.
From the MuSCAT3 data however, we do know that the transit
was observed, and the increase in radial velocity seen shortly after
ingress is more consistent with a prograde or polar orbit than a
retrograde orbit.  Fixing the orbit to be either exactly prograde or
exactly retrograde, we find $\Delta {\rm BIC} = {\rm BIC}_{\rm
retrograde} - {\rm BIC}_{\rm trend} = 18.0$; the retrograde case is
ruled out on this basis.
% More data will be needed however to
% make a more precise measurement of the stellar obliquity.

@@

\software{
  %\texttt{arviz} \citep{arviz_2019},
  \texttt{altaipony} \citep{ilin_flares_2021},
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  %\texttt{astroplan} \citep{astroplan2018},
	%\texttt{AstroImageJ} \citep{collins_astroimagej_2017},
  \texttt{astropy} \citep{astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
  %\texttt{ceres} \citep{brahm_2017_ceres},
  %\texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019},
  \texttt{corner} \citep{corner_2016},
  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
  dependencies \citep{exoplanet:agol20, exoplanet:kipping13, exoplanet:luger18,
   	exoplanet:theano},
	%\texttt{gala} \citep{gala,PriceWhelan_2017_gala_zenodo},
	%\texttt{IDL Astronomy User's Library} \citep{landsman_1995},
  %\texttt{IPython} \citep{perez_2007},
	%\texttt{isochrones} \citep{morton_2015_isochrones},
	%\texttt{lightkurve} \citep{lightkurve_2018},
  %\texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  %\texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  %\texttt{numpy} \citep{walt_numpy_2011}, 
  %\texttt{pandas} \citep{mckinney-proc-scipy-2010},
  %\texttt{pyGAM} \citep{serven_pygam_2018_1476122},
  \texttt{PyMC3} \citep{salvatier_2016_PyMC3},
  %\texttt{radvel} \citep{fulton_radvel_2018},
  %\texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001},
  \texttt{TESS-point}  \citep{burke_2020},
  %\texttt{tesscut} \citep{brasseur_astrocut_2019},
	%\texttt{VESPA} \citep{morton_efficient_2012,vespa_2015},
  %\texttt{webplotdigitzer} \citep{rohatgi_2019},
  \texttt{wotan} \citep{hippke_wotan_2019}.
}
\

@@

The \texttt{v0.6} CDIPS target catalog (Table~\ref{tab:v06}) includes stars
that are young, age-dated, and age-dateable.  By ``age-dateable'', we mean that
the age should be measurable at greater precision than a typical FGK field star
using isochronal, gyrochronal, or spectroscopic techniques.
As in
\citet{bouma_cdipsI_2019}, we collected stars that met these criteria
from across the literature.  Table~\ref{tab:metadata} gives a list of
the studies included, and brief summary statistics.
The age measurement methodologies adopted by each study differ: in many,
spatial and kinematic clustering has been performed on the Gaia data,
and ensemble isochrone fitting of the resulting clusters has been performed
(typically focusing on the turn-off).
In other studies however, the claim of youth is based on the location of a
single star in the color-absolute magnitude diagram, or on spectroscopic
information.

@@

Figure~\ref{fig:XYZvtang} shows stars reported by
\citet{kounkel_untangling_2019} to be in the group ``Theia 73'', which
was cross-matched by Kounkel \& Covey as being ``Stephenson 1''.
\citet{kounkel_untangling_2019} reported \noriginal\ stars to be
present in this cluster.  For our Figure, galactic positions were
calculated and plotted only for stars with parallax signal-to-noise
exceeding 20.  The location of the Sun is shown on the plots.  The
smattering of reported cluster members (gray and black points) has a
significantly different structure that the cluster initially
identified by \citet{stephenson_possible_1959} and corroborated by
\citet{eggen_photometric_1968}.  While the non-uniform ``clumps''
might be part of a real structure, they could also be an artifact of
the data processing steps performed by
\citet{kounkel_untangling_2019}.  We therefore opted to only consider
stars in the immediate kinematic and spatial vicinity of \sn.  The
tangential velocities relative to \sn\ are shown in the bottom right
panel.  These are computed by assuming that every star has the same
three-dimensional spatial velocity as \sn, where we assume a systemic
radial velocity of $-16.7 \pm 0.2$\,\kms\ based on the HIRES
spectra.  The
relevant projection effects are then taken into account, as discussed
by {\it e.g.}, \citet{Meingast2021} and \citet{bouma_2021_ngc2516}.
We performed the actual selection by then manually drawing lassos with
the interactive \texttt{glue} visualization tool
\citep{beaumont_2014_13866} in the four projections shown in
Figure~\ref{fig:XYZvtang}.  While other cluster members likely exist
outside of our selection region (and our selection also includes some
field star interlopers), our aim is to verify the existence of the
cluster in the vicinity of Kepler\,1627, and to measure its age.  The
procedure we have adopted enables both tasks.

@@

		\vspace{-0.1cm}
		\subfloat{
			\includegraphics[width=0.55\textwidth]{f6.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler 1627 is a binary.} {\it Top:} High-resolution imaging
    from Gemini-North/`Alopeke ({\it left}) and Keck/NIRC2 ({\it
    right}) shows an $\approx$M2V companion at $\rho \approx
    0\farcs16$, which corresponds to a projected separation of
    $53\pm4$\,au.  {\it Bottom:} Gaia EDR3 renormalized unit weight
    error (RUWE) point estimates for Kepler\,1627A and other members
    of the $\delta$\,Lyr cluster reported by \citet{KounkelCovey2019}.
    Since other members of the cluster with similar brightnesses have
    comparable degrees of photometric variability, the high RUWE
    suggests that Kepler\,1627 is an astrometric binary. 
    \label{fig:kep1627binary}
	}
\end{figure*}

@@

Figure~\ref{fig:flarestats} shows the results.  The vertical lines in
the figure show the planetary orbital period, the synodic period
$P_{\rm syn} = (P_{\rm rot}^{-1} - P_{\rm orb}^{-1})^{-1}$, and linear
combinations thereof.  The tidal period (half the synodic
period) is not shown.  The bins are logarithmically spaced to give 100
bins between the minimum and maximum ordinate values.  The gray bands
express the range of values observed from the Poissonian draws.  While
it does seem like an odd coincidence for peaks in the observed
flare arrival time distribution to coincide with the locations of
these ``special intervals'', the statistical evidence for a
non-Poissonian process driving the flares does not seem especially
overwhelming.  More quantitatively, the peaks observed at the orbital and
synodic periods are within the $\pm 2$-$\sigma$ range of a Poissonian
process, and those at $P_{\rm orb}+P_{\rm syn}$ and $P_{\rm
orb}+2P_{\rm syn}$ are only slightly above this range.  With that
said, future analyses of these data by investigators with more
knowledge of this topic could very well yield more quantitative
insights.
Such analyses should keep in mind an important caveat:
the amplitude
distribution of M-dwarf flares extends up to many times the quiescent
flux \citep[see Figure~7 of][]{gunther_2020}.  A flare on
Kepler\,1627B producing double its quiescent white-light flux would yield
a $\approx$1\% apparent amplitude.
Such flares could represent a significant fraction
of those in the Kepler observations.
